\section{Dirichlet's Integral}

\begin{enumerate}

    % --- Statement and basic convergence ---

  \item State Dirichlet's integral:
    \[
      \int_0^\infty \frac{\sin x}{x}\,dx.
    \]
    What is its value?
  \item Why is the integrand not actually singular at $x=0$? Compute
    \[
      \lim_{x\to 0} \frac{\sin x}{x}.
    \]
  \item Does
    \[
      \int_0^\infty \left|\frac{\sin x}{x}\right|dx
    \]
    converge? What does this tell you about the convergence of Dirichlet's integral?
  \item Use integration by parts on
    \[
      \int_1^R \frac{\sin x}{x}\,dx
    \]
    to show that the limit as $R\to\infty$ exists.

    % --- Scaling and simple variants ---

  \item For $a>0$, compute
    \[
      \int_0^\infty \frac{\sin(ax)}{x}\,dx
    \]
    by the substitution $u=ax$.
  \item What happens to the previous integral when $a=0$?
  \item What happens when $a<0$? Use the oddness of $\sin$ to determine the sign.
  \item Compare
    \[
      \int_0^\infty \frac{\sin(ax)}{x}\,dx
      \quad\text{and}\quad
      \int_0^\infty \sin(ax)\,dx.
    \]
    Why does the factor $\tfrac1x$ matter so much?

    % --- Introducing a parameter ---

  \item Define
    \[
      F(a)=\int_0^\infty e^{-ax}\frac{\sin x}{x}\,dx,
      \qquad a>0.
    \]
    Why is this integral easier to handle than
    \[
      \int_0^\infty \frac{\sin x}{x}\,dx
    \]
    directly?
  \item Differentiate $F(a)$ with respect to $a$ and show that
    \[
      F'(a)=-\int_0^\infty e^{-ax}\sin x\,dx.
    \]
  \item Compute
    \[
      \int_0^\infty e^{-ax}\sin x\,dx
    \]
    for $a>0$.
  \item Deduce that
    \[
      F'(a)=-\frac{1}{1+a^2}.
    \]
    Integrate this with respect to $a$.
  \item Use the condition
    \[
      \lim_{a\to\infty} F(a)=0
    \]
    to determine the constant of integration.
  \item Show that
    \[
      F(a)=\frac{\pi}{2}-\arctan a=\arctan\frac{1}{a}.
    \]
  \item Let $a\to 0^+$ and recover Dirichlet's integral.
  \item Why is introducing the factor $e^{-ax}$ a useful trick before letting $a\to 0^+$?

    % --- A useful identity ---

  \item Verify the identity
    \[
      \frac{\sin x}{x}=\int_0^1 \cos(tx)\,dt.
    \]
  \item Substitute this identity into
    \[
      \int_0^\infty \frac{\sin x}{x}\,dx.
    \]
    What formal double integral do you obtain?
  \item Why is it dangerous to interchange the order of integration in that double integral without extra justification?

    % --- Laplace transform viewpoint ---

  \item Explain why
    \[
      F(a)=\int_0^\infty e^{-ax}\frac{\sin x}{x}\,dx
    \]
    can be viewed as the Laplace transform of $\dfrac{\sin x}{x}$ evaluated at $a$.
  \item If
    \[
      f(x)=\frac{\sin x}{x},
    \]
    write $F(a)=\mathcal{L}\{f\}(a)$. What does the formula
    \[
      F(a)=\frac{\pi}{2}-\arctan a
    \]
    tell you about $\mathcal{L}\!\left\{\dfrac{\sin x}{x}\right\}(a)$?
  \item Starting from
    \[
      \frac{\sin x}{x}=\int_0^1 \cos(tx)\,dt,
    \]
    use linearity of the Laplace transform to derive
    \[
      \mathcal{L}\!\left\{\frac{\sin x}{x}\right\}(a)
      =
      \int_0^1 \mathcal{L}\{\cos(tx)\}(a)\,dt.
    \]
    Why is this a safer way to use the identity than working directly with
    \[
      \int_0^\infty \frac{\sin x}{x}\,dx?
    \]
  \item Compute
    \[
      \mathcal{L}\{\cos(tx)\}(a)
    \]
    for $a>0$, and use it to show that
    \[
      \mathcal{L}\!\left\{\frac{\sin x}{x}\right\}(a)
      =
      \int_0^1 \frac{a}{a^2+t^2}\,dt.
    \]
    In other words, show that
    \[
      F(a)=\int_0^1 \int_0^\infty e^{-ax}\cos(tx)\,dx\,dt.
    \]
  \item Evaluate
    \[
      \int_0^1 \frac{a}{a^2+t^2}\,dt
    \]
    and recover the formula
    \[
      \mathcal{L}\!\left\{\frac{\sin x}{x}\right\}(a)
      =
      \frac{\pi}{2}-\arctan a.
    \]
  \item Use the Laplace-transform identity
    \[
      \mathcal{L}\{f'\}(a)=a\mathcal{L}\{f\}(a)-f(0)
    \]
    with
    \[
      f(x)=\frac{\sin x}{x}
    \]
    to explain informally why the transform of $\dfrac{\sin x}{x}$ should be related to an arctangent.
  \item Why does the limit
    \[
      \lim_{a\to 0^+}\mathcal{L}\!\left\{\frac{\sin x}{x}\right\}(a)
    \]
    recover Dirichlet's integral?
  \item Compare these two viewpoints:
    differentiating
    \[
      F(a)=\int_0^\infty e^{-ax}\frac{\sin x}{x}\,dx
    \]
    with respect to $a$, and recognizing $F(a)$ as a Laplace transform from the start.
    Why are these really two versions of the same idea?
  \item Which route feels more natural if you already know Laplace transforms well:
    differentiating $F(a)$ first, or rewriting $F(a)$ as a Laplace transform of
    $\dfrac{\sin x}{x}$? Explain your answer.

    % --- Interpretation and checks ---

  \item Why is the value $\pi/2$ plausible from the formula
    \[
      F(a)=\frac{\pi}{2}-\arctan a
    \]
    when $a\to 0^+$?
  \item Explain in words why oscillation of $\sin x$ is essential for convergence on $(1,\infty)$.
  \item Sketch the graph of $\dfrac{\sin x}{x}$ and explain how the alternating positive and negative lobes fit the value of the integral.
  \item Compute
    \[
      \int_0^\infty \frac{\sin(bx)}{x}\,dx
    \]
    for $b>0$, and verify your formula by checking the special case $b=1$.

\end{enumerate}
