\section{Newton's (Newton--Raphson) Method}

\begin{enumerate}

\item What is the goal of a root-finding algorithm?

\item State the Newton method iteration formula for finding a root of a function $f(x)$.

\item How do you obtain the next iterate $x_{n+1}$ from the tangent line?

\item Derive the Newton iteration by applying a first-order Taylor expansion of $f(x)$ around $x_n$.

\item What assumptions about $f(x)$ are required for Newton's method to work?

\item What is meant by an initial guess $x_0$, and why is it important?

\item Define what it means for Newton's method to converge.

\item What is quadratic convergence?

\item Why does Newton's method converge faster near the root than far from it?

\item What happens if $f'(x_n) = 0$ during the iteration?

\item Why is Newton's method considered a local method?

\item Why can Newton's method fail to converge for some initial guesses?

\item Give an example of a function and initial guess where Newton's method diverges.

\item What is meant by the basin of attraction of a root?

\item How does the choice of initial guess affect which root Newton's method converges to?

\item What is a multiple root, and how does it affect convergence of Newton's method?

\item How can Newton's method be modified to handle multiple roots?

\item What stopping criteria can be used to terminate Newton's method?

\item Compare stopping criteria based on $|x_{n+1} - x_n|$ and $|f(x_n)|$.

\item How is Newton method formulated in terms of a vector-valued function $F(x)$?

\item How can Newton's method be extended to systems of nonlinear equations?

\item How do we define the Jacobian matrix $J_F(x)$ for a function $F : \mathbb{R}^n \to \mathbb{R}^n$?

\item Write the Newton iteration formula for solving $F(x) = 0$ in $\mathbb{R}^n$.

\item What role does the Jacobian matrix play in multidimensional Newton's method?

\item What issues arise when the Jacobian is singular or nearly singular?

\item What is a damped (or modified) Newton method?

\item Why might damping improve convergence?

\item How can Newton's method be used to find extrema of a function?

\item How is Newton's method related to solving $f'(x) = 0$?

\item What is the difference between Newton's method for optimization and for root finding?

\item What is the order of convergence of Newton's method compared to secant and bisection methods?

\item What is the secant method, and how does it approximate Newton's method?

\item When might the secant method be preferred over Newton's method?

\item How can automatic differentiation help in implementing Newton's method?

\item What is line search in the context of Newton's method?

\item How can Newton's method behave near inflection points?

\item What happens if the function is not differentiable at the root?

\item Why can Newton's method oscillate between points instead of converging?

\item How can you detect divergence in practice?

\item What are hybrid methods that combine Newton's method with bracketing methods?

\item Why are hybrid methods often preferred in practice?

\item What is the role of scaling in Newton's method for systems?

\item What is meant by the error $e_n = x_n - r$, and how does it evolve in Newton's method?

\item Derive the error recurrence relation for Newton's method near a simple root.

\item What is the goal of Newton's method in the context of optimization?

\item How do we derive Newton's method for finding a local minimum of a scalar function $f(x)$?

\item What role does the gradient $\nabla f(x)$ play in Newton's method?

\item What is the Hessian matrix $\nabla^2 f(x)$ and how is it defined?

\item Write the Newton iteration formula for optimization in $\mathbb{R}^n$.

\item How does Newton's method extend to complex-valued functions?

\item What are basins of attraction in the complex plane?

\item How can we visualize the convergence behavior of Newton's method in the complex plane?

\item How do Newton fractals arise from iterating Newton's method in $\mathbb{C}$?

\item Why do the boundaries between basins of attraction exhibit fractal structure?

\item What are fixed points of the Newton iteration map?

\item Are all fixed points of the Newton map roots of $f(z)$?

\item What are attracting, repelling, and neutral fixed points in this context?

\end{enumerate}
