\subsection{Calculus Vol2 - 6.4 Working with Taylor Series}

\url{https://openstax.org/books/calculus-volume-2/pages/6-4-working-with-taylor-series}

\begin{enumerate}
  \item What is the Taylor series of a function $f$ centered at $x=a$?
  \item What is the Maclaurin series? How does it relate to the Taylor series?
  \item Write the Taylor series of $f$ centered at $a$ using sigma notation.
  \item What is the $n$th Taylor polynomial $T_n(x)$ of a function $f$ centered at $a$?
  \item What is the relationship between the Taylor polynomial $T_n(x)$ and the full Taylor series?
  \item Compute the Maclaurin series of $e^x$.
  \item Compute the Maclaurin series of $\sin x$.
  \item Compute the Maclaurin series of $\cos x$.
  \item Compute the Maclaurin series of $\dfrac{1}{1-x}$ and state its interval of convergence.
  \item How can you obtain the Maclaurin series for $\ln(1+x)$ from the geometric series?
  \item How can you obtain the Maclaurin series for $\arctan x$?
  \item Given a known power series, how can you:
    \begin{enumerate}
      \item Differentiate it term-by-term?
      \item Integrate it term-by-term?
    \end{enumerate}
  \item What happens to the radius of convergence when you differentiate or integrate a power series?
  \item How can you construct the Taylor series for $e^{2x}$ using the known series for $e^x$?
  \item How can you construct the Taylor series for $\sin(3x)$?
  \item How can you construct the Taylor series for $x e^x$?
  \item How can you construct the Taylor series for $\dfrac{x}{1-x^2}$?
  \item How do you find the Taylor series of a function centered at a point $a \neq 0$?
  \item Find the Taylor series of $\ln x$ centered at $x=1$.
  \item What substitution allows you to rewrite $\ln x$ in terms of $\ln(1+u)$?
  \item How can you approximate a function using its Taylor polynomial?
  \item What is Taylor's theorem?
  \item What is the remainder term $R_n(x)$ in Taylor's theorem?
  \item State the Lagrange form of the remainder.
  \item How can you use the remainder term to bound the error of a Taylor approximation?
  \item Suppose $|f^{(n+1)}(x)| \le M$ on an interval containing $a$ and $x$. What inequality bounds $|R_n(x)|$?
  \item How do you determine how large $n$ must be to guarantee a given approximation error?
  \item Use a Taylor polynomial to approximate $e^{0.1}$. How can you estimate the error?
  \item Use a Taylor polynomial to approximate $\sin(0.2)$. How can you estimate the error?
  \item What does it mean for a function to be equal to its Taylor series?
  \item Give an example of a function whose Taylor series converges but does not equal the function.
  \item Why does the Taylor series of $e^x$ converge for all $x$?
  \item Why does the geometric series converge only for $|x|<1$?
  \item How does the factorial in the denominator affect convergence of Taylor series?
  \item When approximating near $x=a$, why is it better to center the Taylor polynomial at $a$ rather than at $0$?
  \item If you need a very accurate approximation near $x=2$, which center should you choose and why?
  \item How does increasing $n$ affect:
    \begin{enumerate}
      \item The accuracy of approximation?
      \item The computational cost?
    \end{enumerate}
  \item What is the difference between a Taylor polynomial and a Taylor series?
  \item How does Taylor series provide a bridge between polynomials and general smooth functions?
\end{enumerate}
