\subsection{Calculus Vol2 - 2.7 Integrals, Exponential Functions, and Logarithms}

\url{https://openstax.org/books/calculus-volume-2/pages/2-7-integrals-exponential-functions-and-logarithms}

\begin{enumerate}
  \item How can the natural logarithm function $\ln x$ be defined using a definite integral?
  \item Why does the usual power rule for integration fail for $\int \frac{1}{x},dx$, and how does the integral definition of $\ln x$ resolve this?
  \item What is the domain of the function $\ln x$ when defined via an integral, and why?
  \item How is $\ln x = \int_1^x \frac{1}{t},dt$ interpreted geometrically?
  \item What is the value of $\ln 1$, and how does it follow from the integral definition?
  \item Is $\ln x$ increasing or decreasing on its domain? How can this be seen from the integral definition?
  \item What is the derivative of $\ln x$, and how does it follow from the Fundamental Theorem of Calculus?
  \item How can you use the definition of $\ln x$ to show it is continuous and differentiable?
  \item How is the number $e$ defined using the natural logarithm?
  \item What special property defines the number $e$ in terms of $\ln x$?
  \item How is the exponential function $e^x$ defined as an inverse function?
  \item What is the derivative of $e^x$, and why is this property significant?
  \item What is the integral of $e^x$?
  \item How do you compute $\int e^{kx},dx$ for a constant $k$?
  \item How are general exponential functions $a^x$ expressed in terms of $e^x$?
  \item What is the formula for $\int a^x,dx$ and how does $\ln a$ appear in it?
  \item How are general logarithmic functions $\log_a x$ expressed using $\ln x$?
  \item What is the derivative of $\log_a x$ in terms of $\ln a$?
  \item What are the key logarithmic properties (product, quotient, power rules), and how can they be justified using integrals?
  \item How can you prove that $\ln(ab) = \ln a + \ln b$ using the integral definition?
  \item How can you prove that $\ln(a^r) = r \ln a$?
\end{enumerate}
