\subsection{Calculus Vol2 - 5.6 Ratio and Root Tests}

\url{https://openstax.org/books/calculus-volume-2/pages/5-6-ratio-and-root-tests}

\begin{enumerate}
  \item Why is the condition $\lim_{n\to\infty} a_n = 0$ not sufficient to guarantee convergence of $\sum a_n$?
  \item Give an example of two series where $a_n \to 0$ in both cases, but one converges and the other diverges.
  \item What does it mean for the terms of a series to approach zero “fast enough”?
  \item State the Ratio Test for a series $\sum a_n$.
  \item Define
    \[
      \rho = \lim_{n\to\infty} \left| \frac{a_{n+1}}{a_n} \right|.
    \]
  \item What conclusion can be drawn if $\rho < 1$ in the Ratio Test?
  \item What conclusion can be drawn if $\rho > 1$ (or $\rho = \infty$) in the Ratio Test?
  \item What happens if $\rho = 1$ in the Ratio Test?
  \item What type of convergence does the Ratio Test establish when $\rho < 1$?
  \item For what kinds of series is the Ratio Test especially useful?
  \item Apply the Ratio Test conceptually: what happens to the ratio $\left|\frac{a_{n+1}}{a_n}\right|$ for factorial-type expressions?
  \item State the Root Test for a series $\sum a_n$.
  \item Define
    \[
      \rho = \lim_{n\to\infty} \sqrt[n]{|a_n|}.
    \]
  \item What conclusion can be drawn if $\rho < 1$ in the Root Test?
  \item What conclusion can be drawn if $\rho > 1$ in the Root Test?
  \item What happens if $\rho = 1$ in the Root Test?
  \item Compare the Ratio Test and Root Test: what is similar about their conclusions?
  \item In what situations is the Root Test particularly useful?
  \item How does the Root Test behave for expressions involving powers like $(b_n)^n$?
  \item What does it mean for a test to be “inconclusive”?
  \item Give an example of a series where the Ratio Test is inconclusive.
  \item Give an example of a series where the Root Test is inconclusive.
  \item Why might one test succeed when another test fails?
  \item What is absolute convergence, and how do these tests relate to it?
  \item Why do both the Ratio and Root Tests use absolute values?
  \item How are these tests useful for power series?
  \item What general strategy can be used to choose an appropriate convergence test for a given series?
  \item When should you consider using the Ratio Test over other tests?
  \item When should you consider using the Root Test over other tests?
  \item What is a good first step before applying either the Ratio or Root Test?
  \item How can simplifying expressions help when applying these tests?
  \item Why are these tests often easier to apply than comparison tests?
  \item Can the Ratio or Root Test determine conditional convergence?
  \item How do these tests relate to geometric series?
  \item How can you sometimes modify a series to make the Root Test easier to apply?
  \item Why is it important to recognize patterns like factorials, exponentials, or powers before choosing a test?
  \item Summarize the decision process after computing $\rho$ in either test.
\end{enumerate}
