\subsection{Calculus Vol2 - 7.5 Conic Sections}

\url{https://openstax.org/books/calculus-volume-2/pages/7-5-conic-sections}

\begin{enumerate}
  \item What is a conic section, and how is it formed geometrically?
  \item What are the four main types of conic sections?
  \item How does slicing a cone at different angles produce different conic sections?
  \item What is the definition of a conic section in terms of a focus and a directrix?
  \item What is a focus, and how is it used to define a conic section?
  \item What is a directrix, and what role does it play in defining conics?
  \item What is eccentricity, and how is it defined as a ratio of distances?
  \item How does the value of eccentricity determine the type of conic (circle, ellipse, parabola, hyperbola)?
  \item What is the eccentricity of a circle, ellipse, parabola, and hyperbola?
  \item What is the geometric definition of a parabola in terms of focus and directrix?
  \item What is the standard equation of a parabola, and what do its parameters represent?
  \item How does the parameter $p$ relate to the vertex and focus of a parabola?
  \item What is the geometric definition of an ellipse?
  \item What is the standard equation of an ellipse centered at $(h,k)$?
  \item What are the major and minor axes of an ellipse?
  \item How are the quantities $a$, $b$, and $c$ related in an ellipse?
  \item Where are the foci located in an ellipse?
  \item What is the geometric definition of a hyperbola?
  \item What is the standard equation of a hyperbola centered at $(h,k)$?
  \item How are the quantities $a$, $b$, and $c$ related in a hyperbola?
  \item Where are the foci and vertices located in a hyperbola?
  \item What are asymptotes, and why are they important for hyperbolas?
  \item What is the general second-degree equation of a conic section?
  \item What is the discriminant $4AC - B^2$, and how is it used to classify conics?
  \item How can you identify a conic section from its general quadratic equation?
  \item How can you convert a general conic equation into standard form?
  \item What role does completing the square play in rewriting conic equations?
  \item How are conic sections represented in polar coordinates?
  \item What is the polar form of a conic section involving eccentricity $e$ and parameter $p$?
  \item How does the equation $r = \frac{ep}{1 \pm e\cos\theta}$ or $r = \frac{ep}{1 \pm e\sin\theta}$ describe conics?
  \item What is the focal parameter $p$, and what is its geometric meaning?
  \item How can you determine the type of conic from its polar equation?
  \item What are the key differences between conics in rectangular form and polar form?
  \item How does changing parameters in the equations affect the shape and position of a conic?
\end{enumerate}
