\subsection{Calculus Vol2 - 2.5 Physical Applications}

\url{https://openstax.org/books/calculus-volume-2/pages/2-5-physical-applications}

\begin{enumerate}
  \item What is a density function, and how can it vary along a rod or region?
  \item How do you compute the mass of a thin rod with variable linear density?
  \item What is the formula for mass in terms of an integral over an interval?
  \item How does the concept of a Riemann sum apply to mass calculations?
  \item How is area density different from linear density?
  \item How do you compute the mass of a two-dimensional region with variable density?
  \item What is radial density, and in what situations is it used?
  \item How does symmetry simplify mass calculations in physical problems?
  \item What is work in the context of physics?
  \item How is work defined in terms of force and displacement?
  \item How can work be approximated using sums of small contributions?
  \item What is the general formula for work done by a variable force?
  \item How do you compute work when the force depends on position?
  \item What is Hooke's Law, and how does it relate force to displacement?
  \item How is work computed when stretching or compressing a spring?
  \item Why does the integral for spring work involve the force function $F(x)=kx$?
  \item How do you set up limits of integration in spring problems?
  \item What is a pumping problem in calculus?
  \item How is work computed when lifting a fluid (e.g., water) from a tank?
  \item How do you model a fluid as a collection of thin horizontal slices?
  \item What quantities must be determined for each slice in a pumping problem?
  \item How do you determine the distance each slice must be lifted?
  \item How does density of a fluid affect the work calculation?
  \item What is the role of weight density in fluid problems?
  \item How do you express the work required to pump fluid as an integral?
  \item What is hydrostatic pressure?
  \item How is pressure related to depth in a fluid?
  \item What units are used for pressure?
  \item How do you compute the force exerted by a fluid on a submerged surface?
  \item How is force related to pressure and area?
  \item How do you model a submerged surface using horizontal strips?
  \item How do you compute the force on each strip?
  \item How is the total force found using an integral?
  \item What assumptions are made about fluid density in hydrostatic problems?
  \item How can changing the shape of a container affect work or force calculations?
\end{enumerate}
