\subsection{Calculus Vol2 - 6.2 Properties of Power Series}

\url{https://openstax.org/books/calculus-volume-2/pages/6-2-properties-of-power-series}

\begin{enumerate}

\item What is the general result about combining two power series
  \[
    \sum_{n=0}^{\infty}c_nx^n\quad\text{and}\quad\sum_{n=0}^{\infty}d_nx^n
  \]
  that converge on the same interval \(I\)? State the conditions for addition, scalar multiplication, and multiplication by a power of \(x\).

\item Suppose two power series converge to functions \(f(x)\) and \(g(x)\) on an interval \(I\). What function does the series
  \[
    \sum_{n=0}^{\infty}(c_n+d_n)x^n
  \]
  converge to on \(I\)?

\item For a power series \(\sum_{n=0}^{\infty}c_nx^n\) that converges to \(f(x)\) on an interval \(I\), what is the power series that converges to \(b\,x^m f(x)\) for a real number \(b\) and integer \(m\ge0\)?

\item If \(\sum_{n=0}^{\infty}c_nx^n\) converges to \(f(x)\) on an interval \(I\), what is the new series that represents \(f(b\,x^m)\) when \(|b\,x^m|\) is in the interval \(I\)?

\item What theorem guarantees that a power series can be differentiated and integrated term-by-term on its interval of convergence? What does this theorem say about the resulting series and their convergence?

\item Given a power series
  \[
    f(x)=\sum_{n=0}^{\infty}c_n(x-a)^n,
  \]
  write the term-by-term differentiated series for \(f'(x)\) in summation form.

\item Given the same \(f(x)\) above, write the term-by-term integrated series representing an antiderivative of \(f(x)\).

\item Does term-by-term differentiation or integration change the radius of convergence of a power series? Explain and describe what can happen at the endpoints.

\item Using the known geometric series for \(\frac{1}{1-x}\), what is the power series representation of \(\frac{1}{(1-x)^2}\) found by term-by-term differentiation? Specify its interval of convergence and endpoint behavior.

\item Find a power series representation for \(f(x)=\ln(1+x)\) by integrating the power series for $f'$ and find its interval of convergence.

\item Find a power series representation for \(f(x)=\tan^{-1}(x)\) by integrating the power series for $f'$ and find its interval of convergence.

\end{enumerate}
