\subsection{Calculus Vol2 - 5.2 Infinite Series}

\url{https://openstax.org/books/calculus-volume-2/pages/5-2-infinite-series}

\begin{enumerate}
  \item What is an infinite series? How is it related to a sequence?
  \item How is an infinite series written using summation notation?
  \item What is the difference between a sequence ${a_n}$ and the series $\sum_{n=1}^{\infty} a_n$?
  \item What is a partial sum of a series? How is the $k$-th partial sum $S_k$ defined?
  \item How can an infinite series be defined as a limit of partial sums?
  \item What does it mean for an infinite series to converge?
  \item What does it mean for an infinite series to diverge?
  \item What is the relationship between the convergence of a series and the convergence of its sequence of partial sums?
  \item What does it mean for a series to diverge to infinity?
  \item How can you determine whether a series converges by examining its partial sums?
  \item What is a geometric series? Write its general form.
  \item What is the common ratio of a geometric series?
  \item Under what condition does a geometric series converge?
  \item What is the formula for the sum of a convergent geometric series?
  \item What happens if the common ratio $r$ of a geometric series satisfies $|r| \geq 1$?
  \item How can you derive the formula for the sum of a geometric series?
  \item What is a telescoping series?
  \item How do terms cancel in a telescoping series?
  \item How can you evaluate the sum of a telescoping series?
  \item Why are telescoping series often easier to evaluate than other series?
  \item Give an example of a telescoping series and describe its behavior.
  \item What is the harmonic series? Write its general form.
  \item Does the harmonic series converge or diverge?
  \item Why is it not sufficient for $a_n \to 0$ to guarantee that $\sum a_n$ converges?
  \item What is the divergence test (nth-term test for divergence)?
  \item If $\lim_{n \to \infty} a_n \neq 0$, what can you conclude about $\sum a_n$?
  \item If $\lim_{n \to \infty} a_n = 0$, what can you conclude about $\sum a_n$?
  \item How are infinite series used in applications such as approximations or modeling?
  \item How does the concept of an infinite series extend the idea of a finite sum?
  \item How can infinite series be used to represent functions?
  \item What is the intuitive meaning of “adding infinitely many terms”?
  \item How does the order of terms affect the value of a finite sum? Does this idea carry over to infinite series?
\end{enumerate}
