\subsection{Calculus Vol2 - 2.6 Moments and Centers of Mass}

\url{https://openstax.org/books/calculus-volume-2/pages/2-6-moments-and-centers-of-mass}

\begin{enumerate}
  \item What is the definition of the center of mass of a system?
  \item How can the center of mass be interpreted physically as a “balancing point”?
  \item What is a moment of a system of masses with respect to a point (e.g., the origin)?
  \item For point masses on a line, how do you compute the total mass?
  \item For point masses on a line, how do you compute the moment with respect to the origin?
  \item How do you compute the center of mass $\bar{x}$ for discrete point masses on a line?
  \item How does the formula for center of mass relate to a weighted average?
  \item For point masses in the plane, how are the moments $M_x$ and $M_y$ defined?
  \item How do you compute the coordinates $(\bar{x}, \bar{y})$ of the center of mass in the plane?
  \item Why does the center of mass depend more heavily on regions with larger mass?
  \item What changes when moving from discrete masses to a continuous mass distribution?
  \item What is a lamina?
  \item What assumption is often made about density when studying laminas?
  \item How is mass computed for a continuous distribution along a line?
  \item How is mass computed for a lamina bounded by a function $f(x)$ on $[a,b]$?
  \item How do you define the moment of a continuous mass distribution using integrals?
  \item How are $M_x$ and $M_y$ computed for a lamina using integrals?
  \item How do you compute the center of mass $(\bar{x}, \bar{y})$ for a lamina?
  \item What is the centroid of a region?
  \item When does the centroid coincide with the center of mass?
  \item Why does constant density simplify center of mass calculations?
  \item How can symmetry be used to determine the center of mass without integration?
  \item Where is the center of mass of a rectangular lamina located?
  \item What role does partitioning (Riemann sums) play in deriving formulas for mass and moments?
  \item How do integrals arise naturally from approximating a lamina by small rectangles?
  \item What is the geometric meaning of $M_x$ and $M_y$?
  \item Why is the center of mass independent of density when density is constant?
  \item How would variable density change the formulas for mass and moments?
  \item How does the concept of center of mass connect to real-world applications (e.g., balance, engineering)?
  \item What is the relationship between center of mass and equilibrium?
  \item How can you check whether your computed center of mass is reasonable using symmetry or intuition?
  \item How does the idea of “balancing point” generalize from 1D to 2D regions?
  \item What are the key steps to solve a typical center of mass problem for a region?
  \item What are the key differences between discrete and continuous mass systems?
  \item How can you set up integrals for regions bounded by curves when finding centers of mass?
\end{enumerate}
