\subsection{Calculus Vol2 - 6.1 Power Series and Functions}

\url{https://openstax.org/books/calculus-volume-2/pages/6-1-power-series-and-functions}

\begin{enumerate}
  \item What is the general form of a power series centered at \(x=0\)?
  \item Write the general form of a power series centered at \(x=a\).
  \item Explain in your own words why a power series can be thought of as an “infinite polynomial.”
  \item Give two examples of power series centered at \(x=0\) with explicit formulas for their coefficients \(c_n\).
  \item What does it mean for a power series to be “centered at” a specific point?
  \item State the three possible convergence behaviors of a power series centered at \(x=a\).
  \item Define the \emph{interval of convergence} for a power series.
  \item Define the \emph{radius of convergence} of a power series.
  \item Why does every power series always converge at its center?
  \item Using the geometric series
    \[
      \sum_{n=0}^\infty x^n,
    \]
    determine its interval and radius of convergence.
  \item How can the Ratio Test be used to help find the radius of convergence of a power series?
  \item True/False: If a power series converges for some value \(x_0\), then it converges for all \(x\) with \(|x-a|<|x_0-a|\). Explain your answer.
  \item What is the basic idea behind representing a given function \(f(x)\) with a power series?
  \item Give an example of a function that can be expressed with a power series based on geometric series manipulation.
  \item How would you represent the function \(\frac{1}{1-x}\) as a power series?
  \item Describe why it is sometimes necessary to truncate a power series when approximating a function in practice.
  \item Explain the relationship between power series and functions that are infinitely differentiable near their center.
  \item For a power series with finite radius of convergence \(R\), what can be said about convergence at the endpoints \(x=a\pm R\)?
  \item How are the endpoints of the interval of convergence typically tested if the Ratio Test is inconclusive?
  \item What implications does the convergence of a power series have for the differentiability and integrability of the represented function on its interval of convergence?
\end{enumerate}
