\subsection{Calculus Vol2 - 5.1 Sequences}

\url{https://openstax.org/books/calculus-volume-2/pages/5-1-sequences}

\begin{enumerate}
  \item What is an infinite sequence? How is it typically denoted?
  \item How can a sequence be interpreted as a function? What is its domain?
  \item What is the index of a sequence, and what role does it play?
  \item What is an explicit formula for a sequence? Give an example.
  \item What is a recursive definition of a sequence? How does it differ from an explicit formula?
  \item Given a recursive sequence, how can you compute its first few terms?
  \item What does it mean to graph a sequence? How does it differ from graphing a function?
  \item What is the limit of a sequence?
  \item What does it mean for a sequence ${a_n}$ to converge to a number $L$?
  \item Write the formal $\epsilon$–$N$ definition of convergence of a sequence.
  \item What does it mean for a sequence to diverge?
  \item What are some different ways a sequence can diverge?
  \item What does it mean for a sequence to diverge to infinity? To negative infinity?
  \item Why does changing a finite number of terms of a sequence not affect its convergence?
  \item How can limits of functions be used to determine limits of sequences?
  \item State the theorem relating $\lim_{x\to\infty} f(x)$ and $\lim_{n\to\infty} a_n$ when $a_n = f(n)$.
  \item Evaluate $\lim_{n\to\infty} \frac{1}{n}$ using a function-based argument.
  \item What happens to $r^n$ as $n \to \infty$ when:
    \begin{itemize}
      \item $0 < r < 1$?
      \item $r = 1$?
      \item $r > 1$?
    \end{itemize}
  \item How can limit laws be applied to sequences?
  \item How do you find the limit of a sequence that is a sum or product of simpler sequences?
  \item What is a bounded sequence?
  \item What does it mean for a sequence to be increasing? Decreasing?
  \item What is a monotonic (monotone) sequence?
  \item State the Monotone Convergence Theorem.
  \item Why is the Monotone Convergence Theorem useful?
  \item Give an example of a sequence that is bounded and increasing.
  \item Give an example of a sequence that is unbounded.
  \item Give an example of a sequence that oscillates and does not converge.
  \item How can you determine convergence from the behavior of the terms as $n \to \infty$?
\end{enumerate}
