\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath, amssymb, amsthm}

\hypersetup{
    pdftitle={Active Recall Questions},
    pdfauthor={Mathematics Study Notes},
    pdfsubject={Mathematics},
    pdfkeywords={Mathematics, Active Recall, Self-Check Questions},
    pdfcreator={LaTeX},
    pdfproducer={pdfLaTeX}
}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}

\urlstyle{same}

\title{Active Recall Questions}
\author{Mathematics Study Notes}
\date{\today}

\setcounter{tocdepth}{1}

\begin{document}

\maketitle

\section{Introduction}

Mathematics is not a subject that can be mastered through passive reading alone. True understanding requires the ability to retrieve concepts, definitions, and problem-solving strategies from memory. One of the most effective techniques for achieving this is \emph{active recall}, especially when implemented through a structured list of self-check questions.

\subsection{What is Active Recall?}

Active recall is the process of deliberately retrieving information from memory rather than re-exposing oneself to it. Instead of rereading notes or textbooks, the learner attempts to answer questions, reconstruct proofs, or solve problems without looking at the solution.

In mathematics, this might include:
\begin{itemize}
    \item Stating definitions (e.g., convergence of a series),
    \item Recalling theorems (e.g., the Integral Test),
    \item Re-deriving formulas,
    \item Solving representative problems from memory.
\end{itemize}

\subsection{Role of Self-Check Questions}

A list of self-check questions provides structure to active recall. These questions act as prompts that guide the learner through the essential components of a topic. For example, in studying infinite series, one might ask:
\begin{itemize}
    \item What is the definition of convergence?
    \item When can the Integral Test be applied?
    \item Why does removing finitely many terms not affect convergence?
\end{itemize}

Such questions ensure that the learner engages with both conceptual understanding and procedural knowledge.

\subsection{Why It Works}

Active recall strengthens memory through effortful retrieval. Each time information is successfully recalled, the neural pathways associated with that knowledge become more robust. This leads to:
\begin{itemize}
    \item Improved long-term retention,
    \item Faster recall during problem solving,
    \item Better ability to connect different concepts.
\end{itemize}

Moreover, attempting to answer questions reveals gaps in understanding. These gaps are often invisible during passive review but become immediately apparent during recall attempts.

\clearpage

\tableofcontents

\clearpage

\input{openstax/_index}
\input{mc/_index}
\input{misc/_index}
\input{numeric/_index}
\input{video/_index}

\end{document}
