\section{Parametric vs Implicit Curves}

\subsection{Core understanding}

\begin{enumerate}
  \item What is the difference between a parametric representation and an implicit representation of a curve?
  \item What does each representation emphasize: generation of points or membership of points?
\end{enumerate}

\subsection{Parametric $\to$ Implicit}

\begin{enumerate}[resume]
  \item Given $x = x(t)$ and $y = y(t)$, what does it mean to eliminate the parameter?
  \item Can every parametric curve be written in the form $F(x,y) = 0$? What assumptions are needed?
  \item What are examples where eliminating the parameter is:
    \begin{itemize}
      \item easy?
      \item difficult or impossible in closed form?
    \end{itemize}
  \item Why might the resulting implicit equation not be unique?
\end{enumerate}

\subsection{Implicit $\to$ Parametric}

\begin{enumerate}[resume]
  \item What does it mean to parametrize a curve defined by $F(x,y) = 0$?
  \item What condition on $F$ guarantees a local parametrization?
  \item How does the Implicit Function Theorem justify this?
  \item What role does the condition $\nabla F \neq 0$ play?
\end{enumerate}

\subsection{Local vs Global behavior}

\begin{enumerate}[resume]
  \item What is the difference between a local and a global parametrization?
  \item Why can an implicit curve be parametrized locally but not globally?
\end{enumerate}

\subsection{Failure modes / limitations}

\begin{enumerate}[resume]
  \item Why can’t some implicit curves be written as a single function $y = f(x)$?
  \item What issues arise from:
    \begin{itemize}
      \item multiple branches?
      \item self-intersections?
      \item cusps?
    \end{itemize}
  \item Can a curve with multiple disconnected components be described by a single parametrization?
\end{enumerate}

\subsection{Conceptual insight}

\begin{enumerate}[resume]
  \item Why is it easier to go from parametric to implicit than the other way around?
  \item How does an implicit equation define a level set?
  \item How do these ideas connect to level curves and gradients?
\end{enumerate}

\subsection{Deeper reflection}

\begin{enumerate}[resume]
  \item Can you think of a curve that:
    \begin{itemize}
      \item has a simple parametrization but a complicated implicit form?
      \item has a simple implicit form but requires multiple parametrizations?
    \end{itemize}
  \item What does this tell you about the trade-offs between representations?
\end{enumerate}
