\section*{Jacobian Matrix and Determinant}

\subsection*{Basic Definitions}

\begin{enumerate}

\item Let $F : \mathbb{R}^n \to \mathbb{R}^m$ be given by
  \[
    F(x_1,\dots,x_n) = (f_1(x),\dots,f_m(x)).
  \]
  What is the definition of the \emph{Jacobian matrix} $J_F(x)$?

\item Write explicitly the Jacobian matrix:
  \[
    J_F(x) = \left( \frac{\partial f_i}{\partial x_j} \right).
  \]
  What are its dimensions?

\item In which case is the Jacobian matrix square?

\item When $m = n$, how is the \emph{Jacobian determinant} defined?

\item What does the notation
  \[
    \det J_F(x)
  \]
  represent?

\end{enumerate}

\subsection*{Jacobian as Derivative}

\begin{enumerate}

\item How is the Jacobian matrix related to the total derivative (Fréchet derivative) of a function $F : \mathbb{R}^n \to \mathbb{R}^m$?

\item State the linear approximation formula:
  \[
    F(x+h) \approx F(x) + J_F(x)h.
  \]

\item What does the Jacobian matrix represent geometrically at a point?

\item What condition on $J_F(x)$ ensures that $F$ is locally invertible near $x$?

\end{enumerate}

\subsection*{Chain Rule}

\begin{enumerate}

\item Let $F : \mathbb{R}^n \to \mathbb{R}^m$ and $G : \mathbb{R}^m \to \mathbb{R}^p$.
  State the multivariable chain rule for Jacobians:
  \[
    J_{G \circ F}(x) = ?
  \]

\item When $n=m=p$, what is the corresponding formula for determinants?

\item Why does this imply
  \[
    \det J_{G \circ F}(x)
    =
    \det J_G(F(x)) \cdot \det J_F(x)?
  \]

\end{enumerate}

\subsection*{Geometric Interpretation}

\begin{enumerate}

\item How does the Jacobian determinant describe local volume scaling?

\item What does it mean if $\det J_F(x) > 0$?

\item What does it mean if $\det J_F(x) < 0$?

\item What does it mean if $\det J_F(x) = 0$?

\item How does the absolute value $|\det J_F(x)|$ relate to infinitesimal volume elements?

\end{enumerate}

\subsection*{Change of Variables in Integration}

\begin{enumerate}

\item State the change-of-variables formula in $\mathbb{R}^n$:
  \[
    \int_{F(U)} g(y)\,dy
    =
    \int_U g(F(x))\, |\det J_F(x)| \, dx.
  \]

\item Why is the absolute value necessary?

\item What conditions must $F$ satisfy for the change-of-variables formula to hold?

\item Compute the Jacobian determinant for the transformation from Cartesian to polar coordinates:
  \[
    x = r\cos\theta, \quad y = r\sin\theta.
  \]

\item Why does the area element become
  \[
    dx\,dy = r\,dr\,d\theta?
  \]

\end{enumerate}

\subsection*{Special Cases and Examples}

\begin{enumerate}

\item Compute the Jacobian matrix of
  \[
    F(x,y) = (x^2 y, e^{xy}).
  \]

\item Compute the Jacobian determinant of
  \[
    F(x,y) = (u,v)
  \]
  where
  \[
    u = x+y, \quad v = x-y.
  \]

\item For a linear transformation $F(x)=Ax$, what is $J_F(x)$?

\item How is $\det J_F(x)$ related to $\det A$ in the linear case?

\item If $F$ is a rotation in $\mathbb{R}^2$, what is its Jacobian determinant?

\end{enumerate}

\subsection*{Inverse Function Theorem}

\begin{enumerate}

\item State the inverse function theorem in terms of the Jacobian determinant.

\item Why does $\det J_F(x_0) \neq 0$ imply local invertibility?

\item How is the Jacobian of the inverse function expressed in terms of $J_F$?

\end{enumerate}

\subsection*{Higher Concepts}

\begin{enumerate}

\item How does the Jacobian generalize the derivative of a single-variable function?

\item In what sense is the Jacobian matrix the best linear approximation?

\item How does the determinant relate to orientation?

\item What is the Jacobian in the context of manifolds and coordinate changes?

\item How does the Jacobian relate to differential forms?

\end{enumerate}
