\section{Euler's Method}

\subsection{Fundamental Concepts}
\begin{enumerate}
  \item What problem does Euler's method aim to solve? State the general form of an initial value problem.
  \item What is meant by a numerical approximation to a solution of an ODE?
  \item What role does the step size $h$ play in Euler's method?
\end{enumerate}

\subsection{Geometric and Intuitive Understanding}
\begin{enumerate}[resume]
  \item What is the geometric interpretation of Euler's method in terms of tangent lines?
  \item How would you visualize the steps of Euler's method on a slope field?
\end{enumerate}

\subsection{Derivation and Formulation}
\begin{enumerate}[resume]
  \item Starting from the differential equation $y'(x) = f(x,y)$, derive the Euler update formula.
  \item Write the recursive formula for Euler's method, defining all variables involved.
  \item Given an initial condition $y(x_0) = y_0$, how do you compute $y_1$ using Euler's method?
  \item How do you compute $y_{n+1}$ from $y_n$ in Euler's method?
\end{enumerate}

\subsection{Error Analysis and Accuracy}
\begin{enumerate}[resume]
  \item What is the local truncation error in Euler's method?
  \item What is the global truncation error in Euler's method?
  \item What is the order of accuracy of Euler's method?
  \item How does decreasing the step size $h$ affect the accuracy of Euler's method?
  \item What is the trade-off between accuracy and computational cost in Euler's method?
  \item What types of errors can accumulate in Euler's method over many steps?
  \item How can you estimate the error in Euler's method during computation?
\end{enumerate}

\subsection{Stability and Limitations}
\begin{enumerate}[resume]
  \item What is meant by stability in the context of numerical methods for ODEs?
  \item Why can Euler's method become unstable for certain differential equations?
  \item Give an example of a differential equation where Euler's method performs poorly.
  \item What is a stiff differential equation, and why is Euler's method problematic for such equations?
  \item What happens if the function $f(x,y)$ is not smooth? How does this affect Euler's method?
  \item What are common pitfalls when using Euler's method in practice?
\end{enumerate}

\subsection{Variants and Improvements}
\begin{enumerate}[resume]
  \item What is the difference between explicit Euler and implicit Euler methods?
  \item Write the update formula for the implicit Euler method.
  \item What advantage does the implicit Euler method have over the explicit version?
  \item How can you modify Euler's method to improve accuracy (e.g., midpoint or improved Euler methods)?
  \item What is the idea behind the Heun method (improved Euler method)?
\end{enumerate}

\subsection{Theoretical Connections}
\begin{enumerate}[resume]
  \item How does Euler's method relate to the Taylor series expansion of the solution?
  \item What term(s) of the Taylor series does Euler's method include or neglect?
\end{enumerate}

\subsection{Extensions and Generalizations}
\begin{enumerate}[resume]
  \item Can Euler's method be used for systems of differential equations? How?
  \item How does Euler's method behave when applied backward in time (negative step size)?
\end{enumerate}

\subsection{Euler's Method as Integration}
\begin{enumerate}[resume]
  \item What is the standard form of an ordinary differential equation involving a function \( y(t) \)?
  \item How can the differential equation \( \frac{dy}{dt} = f(t,y) \) be rewritten as an equivalent integral equation?
  \item What does the integral \( \int_{t_n}^{t_{n+1}} f(s, y(s))\,ds \) represent conceptually?
  \item Why is the integral form of the solution exact, even though we may not know \( y(s) \)?
  \item What is the main difficulty in computing the integral \( \int_{t_n}^{t_{n+1}} f(s, y(s))\,ds \) exactly?
  \item What approximation is made in the Forward Euler method for the integrand \( f(s, y(s)) \)?
  \item What is the geometric interpretation of approximating \( f(s, y(s)) \) by \( f(t_n, y(t_n)) \)?
  \item How does this approximation simplify the integral over the interval \( [t_n, t_{n+1}] \)?
  \item How do we define the step size \( h \), and what role does it play?
  \item How do we derive the Forward Euler update formula from the approximated integral?
  \item Why can we interpret the Forward Euler method as a left-endpoint Riemann sum?
  \item In what sense is Forward Euler performing “integration” of the differential equation?
  \item Why does assuming a constant slope over the interval introduce error?
\end{enumerate}
